\vskip-0.6in \Large Political Uncertainty

### 2016-01-28 GS-extension.tex
add intuiton for what positive X,Y,Z means
add subsection on 3 NNBs

		\begin{center}
		or 
		\end{center}
		\[
		  \beta z - \al + b(z) > 0
		\]
		\item If $\al > 0$, legislators on average are biased against B.
			\begin{itemize}
				\item If $\al < 0$, legislators on average are biased in favor of B.
				\item If $\al$ is negative enough, bribe only legislator furthest to the left (most against B)
			\end{itemize}
\end{itemize}

@@

>>>>

		\begin{center}
		or 
		\end{center}
		\[
		  \beta z - \al + b(z) > 0
		\]
		\item If $\al > 0$, legislators on average are biased against B.
			\begin{itemize}
				\item If $\al < 0$, legislators on average are biased in favor of B.
				\item If $\al$ is negative enough, bribe only legislator furthest to the left (most against B)
			\end{itemize}
		\item If $X,Y,$ or $Z$ is positive, it means the probability of legislator $0,\frac{1}{2},$ or $-\frac{1}{2}$ voting for the status quo / against the new proposal / with interest group B is greater than $0.5$.
\end{itemize}

@@

\newpage
\subsection{All Three Bribes are Non-negative}
In many cases all three bribes are non-negative. Here are very loose results
\begin{itemize}
	\item I always observe that $X=Y=Z$. I think it's easy to show this analytically.
	\item From the FOCs, when $X$ and $Y$ are non-negative, it can be shown that a set of inequalities just below Equations~\ref{eq:1} and \ref{eq:2} must hold.
	\item The SOCs when 0 non-negativity constraints bind are on the 3x3 matrix of second derivatives. There are three conditions:
		\[
		  \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2} \left\{\frac{\partial^2 L}{\partial b(0)^2} \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2} - \left[\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)}\right]^2 \right\} \leq 0
		\]
		\[
		  \frac{\partial^2 L}{\partial b(0)^2} \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2} - \left[\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)}\right]^2 \geq 0
		\]
		\[
		  \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2} \leq 0
		\]
		The last one says that $Y$ must be non-negative. The first and second together say that $Z$ must be non-negative.
	\item $Y$ non-negative combined with the inequalities below Equations ~\ref{eq:1} and \ref{eq:2} tells us that $X=Y > 0$.
	\item Similar logic that leads to those inequalities can be used to derive analagous inequalities for $X$ and $Z$ (or $Y$ and $Z$). Then $Z$ non-negative tells us $Z=Y>0$ so that $X=Y=Z >0$.
\end{itemize}

\vskip.3in
Now as to when this case occurs
\begin{itemize}
	\item When $X=Z$ (the two left-most legislators), bribe to $\frac{1}{2}$ is added in before $X$ would move to the right of $Y$, i.e. when $X \rightarrow 0.5$.
	\item This is NOT the case when $X$ and $Y$ are the two non-negative bribes. They can get very large before the left-most legislator is bribed.
\end{itemize}
